Species motif participation provides unique information about species risk of extinction

### 2023-04-03 manuscript/JAE_reply.tex

                \textbf{R:} Proportion of role is the proportion of the species' motif role made up by the particular motif in each panel. [[Ummm this is kind of dumb. Will a caption rewrite fix it?]]

>>>>

                \textbf{R:} Proportion of role is the proportion of the species' motif role made up by the particular motif in each panel. This misunderstanding seems linked to a general difficulty in understanding precisely how we define motif roles. To help remedy this, we have now added motif role vectors to Figure 1 to make it explicit how counts of motifs are translated into vectors of normalised motif frequencies. These frequencies are equivalent to the proportion of a species' total motif participation made up by each motif. We also now use the perminology ``proportion of motif in role'' and ``proportion of motif in network profile'' in the axis labels of Figs. 2, 3, and 5 for consistency.
